APPM report - Draft

### 2022-12-20 paper_version/main.tex
fix some typo

The Debye length $\lambda_D$, as a key characteristic coefficient of plasmas, may range over many orders of magnitude. The induced singularly perturbed problem is a challenge for plasma simulations. Recently so called asymptotic-preserving (AP) schemes, which target such problems, are studied widely. However, in the context of plasma simulations, only AP schemes in one spatial dimension are available. In this work, we construct an AP schemes for Maxwell-Euler equations in three spatial dimensions based on primal-dual meshes and the finite integration technique (FIT) for Maxwell's equations coupled with the finite volume method (FVM) for the fluid equations. Besides, issues like boundary treatment and stabilization in non-conducting regions are tackled. The AP property is verified numerically. We expect this new discretization approach is particularly suited for problems involving multiple scales of the Debye length, e.g. electric arcs.

@@

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the PDE system changes its type\footnote{from hyperbolic to a mixed type}. This poses a challenge for simulations in settings encompassing different regimes. Singularly perturbed problems occur in many physical models, e.g. vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}. It is desirable that numerical schemes are valid for all ranges of scaled parameters. These schemes are then said to be \emph{asymptotic-preserving} (AP). We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g. the mesh size, see also the illustration by a commuting diagram in \cite[][Fig. 1]{jin_2010}. The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are referred to the comprehensive reviews in \cite{jin_2010, degond_2017} for more details about AP schemes.

The content of this paper is organized as follows: In Section 2, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A reformulation of Maxwell's equations in the insulating region is then presented. Section 3 is devoted to the spatial discretization. The concept of primal-dual meshes is introduced based on which FIT and FVM are applied. We discuss the fully-discretized AP scheme in Section 4 and do numerical experiments in Section 5.

@@

\section{Plasma model}

\subsection{The Maxwell-Euler System}
Plasmas consist of electrically charged and neutral particle species that can be treated as fluids. That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating). For more details on fluid models of plasmas, see \cite{chen2016, remi_2014}.

The electromagnetic effects in plasmas are governed by Maxwell's equations, which Maxwell's equations in SI units read
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities\footnote{SI units in square brackets.} are the magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, the electric field $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, the electric displacement field $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, the magnetic field $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, the electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and the electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media in vacuum, which amounts to relying on the linear constitutive relations (namely, material laws):
\begin{equation} \label{equ:material_law}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu\mathbf{H}, 
\end{equation}
where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant in this paper. By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and (\ref{equ:maxwell_gauss_D}) implies the charge conservation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, by taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

Each species in a plasma can be modelled as a compressible fluid by a set of Euler equations, which additionally includes electromagnetic forces as well as other processes, e.g. collisions and recombination. The generic expressions are
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*\in \{e, i, \cdots\}$ represents the indices for electron, ions and other species. The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  charge number $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side takes into account the Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

@@

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems is due to the fact that electric current is the flow of charged particles:
\begin{equation} \label{equ:maxwell_euler_coupling}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation}

@@

First, a reference value for each quantity, e.g. the characteristic length and time scale, is prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the reference pressure is set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the reference value for the specific total energy and enthalpy is set to $\overline{u}^2$. Also taking into account the physical constants, i.e. the reference permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless parameters:
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the dimensionless quantities have the same symbol as the original quantities. For the sake of simplicity, we neglect ionization and recombination but retain collision terms, i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{subequations}
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix} +
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{pmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). \label{equ:rescaling_friction}
\end{equation}

 Assumptions can be made to reduce the number of dimensionless parameters. Following \cite[][Sec. 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_{th,i}$ whereas it is much smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.

@@

In summary, we make the following choices\cite[][sec 2.2]{degond_2017}
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}

@@

with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons take the expression
\begin{align} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align}
The rescaled material laws (\ref{equ:material_law}) keep the same expressions: 
\begin{equation} \label{equ:maxwell_material_law_rescaled}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}, 
\end{equation}
\end{subequations}
but here $\epsilon, \mu$ are the rescaled permittivity and permeability.

We end up with the rescaled Maxwell-Euler system (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) parameterized by $\lambda$.

>>>>

The Debye length $\lambda_D$, as a key characteristic coefficient of plasmas, may range over many orders of magnitude. The induced singularly perturbed problem is a challenge for plasma simulations. Recently so called asymptotic-preserving (AP) schemes, which target such problems, are studied widely. However, in the context of plasma simulations, only AP schemes in one spatial dimension are available. In this work, we construct an AP scheme for Maxwell-Euler equations in three spatial dimensions based on primal-dual meshes and the finite integration technique (FIT) for Maxwell's equations coupled with the finite volume method (FVM) for the fluid equations. Besides, issues like boundary treatment and stabilization in non-conducting regions are tackled. The AP property is verified numerically. We expect this new discretization approach is particularly suited for problems involving multiple scales of the Debye length, e.g. electric arcs.

@@

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed problem, that is, the limiting PDE system changes its type\footnote{The Maxwell-Euler system transits from hyperbolic to a mixed type}. This poses a challenge for simulations in settings encompassing different regimes. Singularly perturbed problems occur in many physical models, e.g. vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, zero-relaxation-limit of kinetic equations \cite{jin_2010} and zero-Mach-limit of compressible flows \cite{degond_2007, haack_2010}. It is desirable that numerical schemes are valid for all ranges of scaled parameters. These schemes are then said to be \emph{asymptotic-preserving} (AP). We discretize a parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g. the mesh size, see also the illustration by a commuting diagram in \cite[][Fig. 1]{jin_2010}. The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are referred to the comprehensive reviews in \cite{jin_2010, degond_2017} for more details about AP schemes.

The content of this paper is organized as follows: In Section \ref{sec:plasma-model}, we give a full description of the underlying equations of the Maxwell-Euler system and its rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A reformulation of Maxwell's equations in the non-conducting region is presented. Section \ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the full AP discretization in Section \ref{sec:full-discretization} and do numerical experiments in Section \ref{sec:numerical_experiment}.

@@

\section{Plasma model} \label{sec:plasma-model}

\subsection{The Maxwell-Euler System}
Plasmas consist of electrically charged and (possibly) neutral particle species that can be treated as fluids. That is, they may be described by the Navier-Stokes equations augmented with source terms for species generation (ionization, recombination), forces (Lorentz force and interspecies friction), and energy (thermal relaxation among species, radiative heat transfer, Ohmic heating). For more details on fluid models of plasmas, see \cite{chen2016, remi_2014}.

The electromagnetic effects in plasmas are governed by Maxwell's equations:
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities\footnote{SI units in square brackets.} are the magnetic flux density $\mathbf{B}[\frac{\text{Wb}}{\text{m}^2}]$, the electric field $\mathbf{E}[\frac{\text{V}}{\text{m}}]$, the electric displacement field $\mathbf{D}[\frac{\text{C}}{\text{m}^2}]$, the magnetic field $\mathbf{H}[\frac{\text{A}}{\text{m}}]$, the electric current density $\mathbf{J}[\frac{\text{A}}{\text{m}^2}]$ and the electric charge density $\rho[\frac{\text{C}}{\text{m}^3}]$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media. Namely, we rely on linear constitutive relations (i.e. material laws):
\begin{equation} \label{equ:material_law}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu\mathbf{H}, 
\end{equation}
where $\epsilon[\frac{\text{F}}{\text{m}}]$ and $\mu[\frac{\text{N}}{\text{A}^{2}}]$ are the permittivity and permeability and assumed to be constant. By taking the time derivative of (\ref{equ:maxwell_gauss_D}) and the divergence of (\ref{equ:maxwell_ampere}), it is easy to see that (\ref{equ:maxwell_ampere}) and (\ref{equ:maxwell_gauss_D}) implies the charge conservation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, by taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

Each species in a plasma can be modelled as a compressible fluid through a set of Euler equations augmented by electromagnetic forces as well as other processes, e.g. collisions and recombination:
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*\in \{e, i, \cdots\}$ labels electrons, ions or other species. The involved fluid quantities are: number density $n_*[\frac{1}{\text{m}^3}]$, particle mass $m_*[\text{kg}]$,  electric charge $q_*[\text{C}]$, velocity $\mathbf{u}_*[\frac{\text{m}}{\text{s}}]$, pressure $p_*[\frac{\text{N}}{\text{m}^2}]$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}[\frac{\text{J}}{\text{kg}}]$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}[\frac{\text{J}}{\text{kg}}]$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*[\frac{\text{A}}{\text{m}^2}]$. All the species are assumed to be ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side takes into account the Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

@@

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems is due to the fact that the flow of charged particles induces electric currents:
\begin{equation} \label{equ:maxwell_euler_coupling}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation}

@@

First, a reference value for each quantity is prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The reference magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the reference pressure is set to $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the reference value for the specific total energy and enthalpy is set to $\overline{u}^2$. Also taking into account the physical constants, i.e. the reference permittivity $\overline{\epsilon}$, the reference permeability $\overline{\mu}$, the light speed $c^2 = (\overline{\epsilon}\overline{\mu})^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, we introduce the following dimensionless parameters:
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_i^{\text{th}}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_i^{\text{th}} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\epsilon k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][Sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the rescaled variables share the same notation as before rescaling. We neglect ionization and recombination but retain collision terms, i.e. $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}). The rescaled Euler-Maxwell system is
\begin{subequations}
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix} +
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{pmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). \label{equ:rescaling_friction}
\end{equation}

 Assumptions can be made to reduce the number of dimensionless parameters. Following \cite[][Sec. 2.2]{degond_2017}, the reference speed $\overline{v}$ is of the same scale as the plasma speed $\overline{u}$ and the thermal speed $v_i^{\text{th}}$ whereas it is much smaller than the light speed $c$. Also, it is assumed that $\eta$ and $\beta$ are of order one and $\xi$ has the same magnitude as $\lambda$.

@@

In summary, we make the following choices \cite[][sec 2.2]{degond_2017}
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}

@@

with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons take the expression:
\begin{align} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align}
The rescaled material laws (\ref{equ:material_law}) keep the same expressions: 
\begin{equation} \label{equ:maxwell_material_law_rescaled}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}. 
\end{equation}
\end{subequations}
Notice here $\epsilon, \mu$ are the rescaled permittivity and permeability.

We end up with the rescaled Maxwell-Euler system: (\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) parameterized by $\lambda$.
